\documentclass[12pt,a4paper]{report}
\pagestyle{empty}
\usepackage{amsmath}
%\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{array}
\bibliographystyle{ieeetr}
\usepackage{float}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{lipsum}
\usepackage{subcaption}
%\usepackage[demo]{graphicx}
%\usepackage{babel,blindtext}
\usepackage{graphicx}
\usepackage[top=.9in, bottom=.9in, left=1.5in, right=.8in]{geometry}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{float}
\usepackage{listings}

\renewcommand{\baselinestretch}{1.5} 
\floatstyle{plaintop}
\restylefloat{table}
\newcommand\Fontvi{\fontsize{8}{10.2}\selectfont}
\usepackage{sidecap}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true, %set true if you want colored links
    linktoc=all,     %set to all if you want both sections and subsections linked
    linkcolor=black,  %choose some color if you want links to stand out
	citecolor=black %http://tex.stackexchange.com/questions/50747/options-for-appearance-of-links-in-hyperref
}
\restylefloat{table}
\begin{document}
\include{front}
\include{certificate_main}
\include{certificate}
 \pagenumbering{roman}
    \setcounter{page}{4} 
\addcontentsline{toc}{chapter}{\bf ACKNOWLEDGEMENT}     
\include{acknowledgement} 
\addcontentsline{toc}{chapter}{\bf ABSTRACT} 
\include{abstract} 
\hypertarget{contents}{}
\tableofcontents
\listoftables
\addcontentsline{toc}{chapter}{\bf LIST OF TABLES}
\listoffigures
\addcontentsline{toc}{chapter}{\bf LIST OF FIGURES}


\clearpage
\pagebreak
\pagestyle{fancy}
\lhead{\small {Evaluation Of Web Security Mechanisms Using Vulnerability Analysis \& Pattern Mining}}
\chead{}
\rhead{}
\lfoot{\small {Department of Computer Science and Engineering, FISAT}}
\cfoot{}
\rfoot{\small {\thepage}}
\renewcommand\headrulewidth{0.4pt}
\renewcommand\footrulewidth{0.4pt}


\pagenumbering{arabic}
\setcounter{page}{1}
\include{introduction}
\include{literature_survey}
\include{methodology}
%\include{exp_result}
\include{conclusion}


\begin{thebibliography}{8}
\addcontentsline{toc}{chapter}{\bf BIBLIOGRAPHY}

\bibitem{1}
cgisecurity.net, www.cgisecurity.com/articles/csrf-faq.shtml\#
whatis, Dec. 2008.

\bibitem{2}
G. Alvarez and S. Petrovic,  ``A New Taxonomy of Web Attacks Suitable for Efficient Encoding,'' Computers and Security, vol. 22,
no. 5, pp. 435-449, July 2003

%H. Chang, D.-Y. Yeung, and Y. Xiong,  ``Super-resolution through neigh-
%bor embedding,'' in Proc. IEEE Conf. Comput. Vis. Pattern Recognit.,
%Jul. 2004, pp. 275–282.


\bibitem{3}
S. Christey and R. Martin,  ``Vulnerability Type Distributions in
CVE,'' Mitre Report, May 2007.

\bibitem{4}
J. Duraes and H. Madeira,  ``Emulation of Software Faults: A Field
Data Study and a Practical Approach,'' IEEE Trans. Software Eng.,
vol. 32, no. 11, pp. 849-867, Nov. 2006.

\bibitem{5}
M.R. Lyu, Handbook of Software Reliability Engineering. IEEE
Computer Society Press \& McGraw-Hill, 1996.

\bibitem{6}
J. Williams and D. Wichers,  ``OWASP Top 10,'' OWASP Foundation, Feb. 2013.

\bibitem{7}
N. Neves, J. Antunes, M. Correia, P. Verissimo, and R. Neves,
 ``Using Attack Injection to Discover New Vulnerabilities,'' Proc.
IEEE/IFIP Int’l Conf. Dependable Systems and Networks, 2006.

\bibitem{8}
J. Fonseca, M. Vieira, and H. Madeira,  ``Testing and Comparing
Web Vulnerability Scanning Tools for SQLi and XSS Attacks,''
Proc. IEEE Pacific Rim Int’l Symp. Dependable Computing, Dec. 2007.

\bibitem{9}
S. Clowes,  ``A Study in Scarlet, Exploiting Common Vulnerabilities in PHP Applications,'' http://www.securereality.com.au/
studyinscarlet.txt, 2013.

\bibitem{10}
B. Livshits and S. Lam,  ``Finding Security Vulnerabilities in Java
Applications with Static Analysis,'' Proc. USENIX Security Symp.,
pp. 18-18, 2005.

\bibitem{11}
M. Buchler, J. Oudinet, and A. Pretschner,  ``Semi-Automatic Security Testing of Web Applications from a Secure Model,'' Proc. Int’l
Conf. Software Security and Reliability, 2012.

\bibitem{12}
S. McConnell, ``Gauging Software Readiness with Defect
Tracking'', IEEE Software, vol. 14, no. 3, May/June 1997.

\bibitem{13}
N. Nagappan, L. Williams, J. Hudepohl, W. Snipes, M. Vouk,
 ``Preliminary Results on Using Static Analysis Tools for Software
Inspection.'' Proc. Int’l Symp. Software Reliability Eng., pp. 429-439,
2004.
\bibitem{14}
OSVDB,  ``Open Sourced Vulnerability Database,'' http://osvdb.
org, May 2013.
\bibitem{15}
D. Powell and R. Stroud,  ``Conceptual Model and Architecture of
MAFTIA,'' Project MAFTIA, Deliverable D21, 2003.

\bibitem{16}
J. Fonseca and M. Vieira,  ``Mapping Software Faults with Web
Security Vulnerabilities,'' Proc. IEEE/IFIP Int’l. Conf. Dependable
Systems and Networks, June 2008

\bibitem{17}
S. Fogie, J. Grossman, R. Hansen, A. Rager, and P. Pektov, XSS
Attacks: Cross Site Scripting Exploits and Defense. Syngress, 2007.
Intell., vol. 32, no. 6, pp. 1127–1133, Jun. 2010.
\bibitem{18}
J. Arlat, A. Costes, Y. Crouzet, J.-C. Laprie, and D. Powell,  ``Fault
Injection and Dependability Evaluation of Fault-Tolerant Systems,'' IEEE Trans. Computers, vol. 42, no. 8, pp. 913-923, Aug.
1993.
\bibitem{19}
T. Scholte et al.,  ``An Empirical Analysis of Input Validation
Mechanisms,'' Proc. ACM Symp. Applied Computing, pp. 1419-1426,
2012.

\bibitem{20}
J. Carreira, H. Madeira, and J.G. Silva,  ``Xception: Software Fault
Injection and Monitoring in Processor Functional Units,'' IEEE
Trans. Software Eng., vol. 24, no. 2, Feb. 1998.

\bibitem{21}
 N. Tomatis, R. Brega, G. Rivera, and R. Siegwart,  ``May You Have
 a Strong (-Typed) Foundation’ Why Strong Typed Programming
 Languages Do Matter,'' Proc. IEEE Int’l Conf. Robotics and
 Automation, 2004.
 
\bibitem{22}
J. Christmansson and R. Chillarege,  ``Generation of an Error Set
that Emulates Software Faults,'' Proc. IEEE Fault Tolerant Computing Symp., 1996.
\bibitem{23}
H Madeira, M. Vieira, and D. Costa,  ``On the Emulation of Software Faults by Software Fault Injection,'' Proc. IEEE/IFIP Int‘l
Conf. Dependable System and Networks, 2000.

\bibitem{24}
M. Cukier, R. Berthier, S. Panjwani, and S. Tan,  ``A Statistical
Analysis of Attack Data to Separate Attacks,'' Proc. Int’l Conf.
Dependable Systems and Networks, pp. 383-392, 2006.

\end{thebibliography}
\end{document}
